Paper Analysis

### 2025-04-28 Paper_WriteUp/Paper_Plots.qmd
updating and cleaning figS1 chunks

```{r figure s1-left}
#| eval: false
data_path <- here("results_2025/lichess2000-2200")

fit_20_22_bullet_prev <- readRDS(file = 
                                   paste0(data_path,
                                          "/all_rated_bullet_model_prev_n1.RDS"))

bullet_20_22 <- readRDS(file = paste0(data_path, "/users_bullet.RDS"))

@@

player_pars <- fit_20_22_bullet_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id")

winner_plot_20_22 <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |> 
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_histinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "2000-2200 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

ggsave(plot = winner_plot_20_22, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "Figure_S1_left.png")), dpi = 600,
       height = 7, width = 7)
```

@@

```{r figure-s1-right}
#| eval: false
data_path <- here("results_2025/lichess2300-2500")

fit_23_25_bullet_prev <- readRDS(file = 
                                   paste0(data_path,
                                          "/all_rated_bullet_model_prev_n1.RDS"))

bullet_23_25 <- readRDS(file = paste0(data_path, "/users_bullet.RDS"))

@@

winner_plot_23_25 <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |> 
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_histinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "2300-2500 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

ggsave(plot = winner_plot_23_25, 
       filename = paste0(here("Paper_WriteUp", "paper_figures",
                              "Figure_S1_right.png")), dpi = 600,
       height = 7, width = 7)
```

>>>>

```{r figure s1-left}
#| eval: false
#read in model
fit_20_22_bullet_prev = readRDS(here("results_revision", "lichess2000-2200", "all_rated_bullet_model_n1.RDS"))

#read in users
bullet_20_22 = readRDS(here("results_revision", "lichess2000-2200", "users_bullet.RDS"))

@@

#draws of winner effects
player_pars <- fit_20_22_bullet_prev$draws() |> 
  as_draws_df() |>
  select(starts_with("beta[")) |>
  pivot_longer(cols = everything()) |>
  mutate(param = stringr::str_extract(name, pattern = "\\d"),
         id = stringr::str_extract(name, pattern = "\\d+]"),
         id = stringr::str_replace(id, "\\]", ""),
         player_id = paste0("beta[", id, "]")) |> 
  mutate(id = as.numeric(id),
         param = as.numeric(param)) |> 
  left_join(player_id, by = "id")

#plot
winner_plot_20_22 <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |> 
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_pointinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "2000-2200 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

#save
ggsave(plot = winner_plot_20_22, 
       filename = here("Paper_WriteUp", "paper_figures", "FigS1_left.png"), dpi = 600,
       height = 7, width = 7)
```

@@

```{r figure-s1-right}
#| eval: false
#read in model
fit_20_22_bullet_prev = readRDS(here("results_revision", "lichess2300-2500", "all_rated_bullet_model_n1.RDS"))

#read in users
bullet_20_22 = readRDS(here("results_revision", "lichess2300-2500", "users_bullet.RDS"))

@@

#plot
winner_plot_23_25 <- player_pars |> 
  filter(param == 2) |> 
  mutate(prob = 1/(1 + exp( -1 * value)) - 0.5) |> 
  ggplot(aes(y = reorder(player_name, prob, FUN = median), x = prob)) +
  stat_pointinterval() +
  labs(x = "Change in Win Probability", y = element_blank(), 
       title = "2300-2500 Cohort") +
  geom_vline(aes(xintercept = 0), col = "red", linetype = "dashed") +
  theme_single_y()

#save
ggsave(plot = winner_plot_23_25, 
       filename = here("Paper_WriteUp", "paper_figures", "FigS1_right.png"), dpi = 600,
       height = 7, width = 7)
```
